---
title: "MATH4753BROSAlab4"
author: "Brandan Rosa"
output: 
    rmarkdown::html_vignette:
vignette: >
  %\VignetteIndexEntry{MATH4753BROSAlab4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(MATH4753BROSAlab4)
```

# Introduction

This package contains an S3 function, "mybiplot", which takes a numeric vector ($x$) and a user-chosen standard deviation value ($k$), compares each value from $x$ to the mean of $x$, and assigns each data point one of the following: "in", "outu", "outl". For those values who fall within $k$ standard deviations of the mean, "in" is assigned. If the data point is greater than $k$, "outu" is assigned, and otherwise "outl" is assigned. These values are ultimately stored into the matrix "inout".

The package also includes two S3 methods for the generics "print" and "summary" which have class "math4753biplot". The method "print.math4753biplot" produces a histogram (from ggplot2) which is colored according to the "inout" status of the data. The "summary.math4753biplot" method summarizes the data according to its "inout" status and produces the mean, median, and IQR.

We will investigate this package using the EPAGAS data set for values of $k = 1$, $k = 2$, and $k = 3$ for the standard deviations.

```{r}
mpg <- epa$MPG
```

# Examples

## For $k=1$

```{r, fig.align = "center", fig.width=8, fig.height=5}
a <- mybiplot(x = mpg, k = 1)

print(a)
summary(a)
```

## For $k=2$

```{r, fig.align = "center", fig.width=8, fig.height=5}
b <- mybiplot(x = mpg, k = 2)

print(b)
summary(b)
```

## For $k = 3$

```{r, fig.align = "center", fig.width=8, fig.height=5}
c <- mybiplot(x = mpg, k = 3)

print(c)
summary(c)
```

We can see that as we choose larger values of $k$, the more data points are classified "in"; which of course makes perfect sense.

